Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-09 article/article.Rmd
Commit 2024-06-09 17:12

For the detection of CE cases we established a baseline of irradiance above which we
characterized each data point as an enhancement event and calculated the over
irradiance (OIR). The OIR is defined as the irradiance difference of the measured
one-minute $\text{GHI}_i$ from the CE identification criterion ($\text{OIR}_i =
\text{GHI}_i - \text{GHI}_\text{CSlim}$), as defined in
Equation\nobreakspace\ref{eq:CE4}.
To have an estimation, and a first insight on the phenomenon, we experimented with
two simple approaches for the reference.  The Haurwitz's model [@Haurwitz1945], which
is as simple clear sky model, and we had already adjusted and had good fit with our
data [@Natsis2023], and the TSI at the top of the atmosphere.  We have tested both
cases by using an appropriate relative threshold and/or an additional constant
offset.  The initial results, showed that we can detect a big portion of the CE
events. These results were helpful, as they are independent from unknown factors, and
helped us to establish some criteria to further improve the CE identification. It was
evident, by inspecting the daily plot of irradiance, that changes on the atmospheric
conditions introduced numerous false positive and false negative results.  To produce
a more accurate reference, we had to take into account more factors that effect the
clear sky radiation. So we used a radiation transfer
model in order to include the effects of ADO and the water vapors.

>>>>

For the detection of CE cases we established a baseline of irradiance above which we
characterized each data point as an enhancement event and calculated the over
irradiance (OIR). The OIR is defined as the irradiance difference of the measured
one-minute $\text{GHI}_i$ from the $\text{GHI}_\text{ref}$ corresponding to
cloud-free atmosphere. 
<!-- CE identification criterion ($\text{OIR}_i =
\text{GHI}_i - \text{GHI}_\text{CSlim}$), as defined in
Equation\nobreakspace\ref{eq:CE4}. -->
First, we tested two simple approaches for the determination of
$\text{GHI}_\text{ref}$: The Haurwitz's model [@Haurwitz1945], which is a simple
clear sky model and was already adjusted and applied to our data [@Natsis2023], and
the total solar irradiance (TSI) at the top of the atmosphere, adjusted for the
Sun-Earth distance.  We have tested both methods by using an appropriate relative
threshold and/or an additional constant offset.  The initial results showed that we
can detect a big portion of the CE events. However, by inspecting the daily plots of
irradiance it became evident that changes on the atmospheric conditions introduced
numerous false positive and false negative results.  To produce a more accurate
reference, we had to take into account more factors that effect the clear sky
radiation. So we used a radiation transfer model in order to include the effects of
ADO and the water vapors.

### 2024-06-09 article/article.tex
Commit 2024-06-09 17:12

For the detection of CE cases we established a baseline of irradiance
above which we characterized each data point as an enhancement event and
calculated the over irradiance (OIR). The OIR is defined as the
irradiance difference of the measured one-minute \(\text{GHI}_i\) from
the CE identification criterion
(\(\text{OIR}_i = \text{GHI}_i - \text{GHI}_\text{CSlim}\)), as defined
in Equation\nobreakspace\ref{eq:CE4}. To have an estimation, and a first
insight on the phenomenon, we experimented with two simple approaches
for the reference. The Haurwitz's model \citep{Haurwitz1945}, which is
as simple clear sky model, and we had already adjusted and had good fit
with our data \citep{Natsis2023}, and the TSI at the top of the
atmosphere. We have tested both cases by using an appropriate relative
threshold and/or an additional constant offset. The initial results,
showed that we can detect a big portion of the CE events. These results
were helpful, as they are independent from unknown factors, and helped
us to establish some criteria to further improve the CE identification.
It was evident, by inspecting the daily plot of irradiance, that changes
on the atmospheric conditions introduced numerous false positive and
false negative results. To produce a more accurate reference, we had to
take into account more factors that effect the clear sky radiation. So
we used a radiation transfer model in order to include the effects of
ADO and the water vapors.

>>>>

For the detection of CE cases we established a baseline of irradiance
above which we characterized each data point as an enhancement event and
calculated the over irradiance (OIR). The OIR is defined as the
irradiance difference of the measured one-minute \(\text{GHI}_i\) from
the \(\text{GHI}_\text{ref}\) corresponding to cloud-free atmosphere.
First, we tested two simple approaches for the determination of
\(\text{GHI}_\text{ref}\): The Haurwitz's model \citep{Haurwitz1945},
which is a simple clear sky model and was already adjusted and applied
to our data \citep{Natsis2023}, and the total solar irradiance (TSI) at
the top of the atmosphere, adjusted for the Sun-Earth distance. We have
tested both cases by using an appropriate relative threshold and/or an
additional constant offset. The initial results, showed that we can
detect a big portion of the CE events. These results were helpful, as
they are independent from unknown factors, and helped us to establish
some criteria to further improve the CE identification. It was evident,
by inspecting the daily plot of irradiance, that changes on the
atmospheric conditions introduced numerous false positive and false
negative results. To produce a more accurate reference, we had to take
into account more factors that effect the clear sky radiation. So we
used a radiation transfer model in order to include the effects of ADO
and the water vapors.
